Understanding the Impact of Socioeconomic and Regional Factors on Health and Educational Outcomes

### 2024-12-15 paper.qmd
more changes

---
title: "Understanding the Impact of Socioeconomic and Regional Factors on Health and Educational Outcomes"
author: "Rishika Randev, Jenny Wu, Uzoma Uwazurike Jr., Shiyue Zhou"
instructor: "Andrea Lane"
institution: "Duke University, IDS 702 Data Modeling and Presentation"
format: pdf
editor: visual
execute:
  echo: false
  warning: false
---

@@

Table 1 displays summary statistics for the predictors in the second model, stratified by school funding adequacy. School funding adequacy counts show that around 66% of the counties in our analysis had under funded schools. Additionally, the number of counties per region indicate an imbalance between categories, with the South region being over represented (holding 60% of all counties), and the East and Northeast holding around 9% of the counties each. Table A1 in the Appendix provides summary statistics for all variables, and shows that both the mean and median for life expectancy are approximately 75 years.

@@

@@

```{r, echo= FALSE, warning = FALSE}
# Running a regression with the imputated data (completed_data) to understand the impact of missing data

@@

```{r, echo=FALSE}
library(ggplot2)
library(GGally)
library(patchwork)

@@

>>>>

---
title: "Understanding the Impact of Socioeconomic and Regional Factors on Health and Educational Outcomes"
author: "Rishika Randev, Jenny Wu, Uzoma Uwazurike Jr., Shiyue Zhou"
instructor: "Andrea Lane"
institution: "Duke University, IDS 702 Data Modeling and Presentation"
format: pdf
header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
fontsize: 10pt
editor: visual
execute:
  echo: false
  warning: false
---

@@

Table 1 displays summary statistics for the predictors in the second model, stratified by school funding adequacy. School funding adequacy counts show that around 66% of the counties in our analysis had underfunded schools. Additionally, the number of counties per region indicate an imbalance between categories, with the South region being over represented (holding 60% of all counties), and the East and Northeast holding around 9% of the counties each. Table A1 in the Appendix provides summary statistics for all variables, and shows that both the mean and median for life expectancy are approximately 75 years.

@@

```{r, echo=FALSE, fig.pos='H'}
library(ggplot2)
library(GGally)
library(patchwork)

@@

```{r, echo= FALSE, warning = FALSE, fig.pos='H'}
# Running a regression with the imputated data (completed_data) to understand the impact of missing data

@@

@@

*Table 3: Logistic Regression Results For School Funding Adequacy Outcome*
